Figures

### 2019-05-21 figures/08_exploratory_dotplot.Rmd
prettyfi hmap labels

```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE}
dt     <- readRDS("../data/dt.rds")
dt_sub <- dt %>% 
  dplyr::select(tp, tn, lake_area_ha:wheat, 
                matches("cultivated_crops")) %>%
  dplyr::select(-row_crop_pct, -ag_pct, -pasture_pct) %>% # rm nlcd
  dplyr::select(-mixed.crop, -matches("other"), -forage, 
                -hu12_ppt_std, -water, -developed, -forest) %>% # rm junk
  dplyr::filter(complete.cases(.)) %>%
  mutate_all(as.numeric) %>%
  data.frame(stringsAsFactors = FALSE)

@@

>>>>

```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE}
pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
dt       <- readRDS("../data/dt.rds")
dt_sub   <- dt %>% 
  dplyr::select(tp, tn, lake_area_ha:wheat, 
                matches("cultivated_crops")) %>%
  dplyr::select(-row_crop_pct, -ag_pct, -pasture_pct) %>% # rm nlcd
  dplyr::select(-mixed.crop, -matches("other"), -forage, 
                -hu12_ppt_std, -water, -developed, -forest) %>% # rm junk
  dplyr::filter(complete.cases(.)) %>%
  mutate_all(as.numeric) %>%
  data.frame(stringsAsFactors = FALSE)

@@

# prettyfi variable labels
pretty_names <- pred_key$pretty[match(names(dt_tp_hmap), pred_key$var)] 
pretty_names <- pretty_names[!is.na(pretty_names)]
names(dt_tp_hmap)[which(!is.na(match(names(dt_tp_hmap), pred_key$var)))] <- 
  pretty_names
pretty_names <- pred_key$pretty[match(row.names(dt_tp_hmap), pred_key$var)] 
pretty_names <- pretty_names[!is.na(pretty_names)]
row.names(dt_tp_hmap)[which(!is.na(match(row.names(dt_tp_hmap), pred_key$var)))] <- 
  pretty_names
